### 2020-09-03 text/manuscript.tex
Remove S2, S3, update Zenodo link

The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013502}.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Full table of sectors.}
\label{S1_File}
{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/industry-index.csv}.

\paragraph*{S2 Full table of ZIP-codes.}
\label{S2_File}
{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/location-index.csv}.

\paragraph*{S3 Data repository.}
\label{S3_URL}
{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v2.0}.

>>>>

The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013863}.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Full table of sectors.}
\label{S1_File}
{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry. ``communication\_share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``affected\_share'' refers to the share of workers in any of the three occupation groups.
